\documentclass[a4paper, oneside, final]{scrartcl}

% === PACKAGES
\usepackage{soul}
\usepackage{scrlayer-scrpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{ltablex}
\usepackage{colortbl}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{hyperref}

% === USER SPECIFIC LATEX COMMANDS
\newenvironment{lyxlist}[1]
{\begin{list}{}
{\settowidth{\labelwidth}{#1}
 \setlength{\leftmargin}{\labelwidth}
 \addtolength{\leftmargin}{\labelsep}
 \renewcommand{\makelabel}[1]{##1\hfil}}}
{\end{list}}

\newcommand{\noun}[1]{\textsc{#1}}

\newcommand{\gray}{\rowcolor[gray]{.90}}

% === PDF SETUP
\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Filip Bielejec - Curriculum Vitae}, pdfauthor={Filip Bielejec}]
%% {hyperref}
%% \hypersetup{linkcolor=black, citecolor=blue, filecolor=black, urlcolor=black}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\urlstyle{rm}

% === DOCUMENT LAYOUT
\geometry{a4paper, textwidth=19cm, textheight=22cm, marginparsep=16cm, marginparwidth=1cm, headheight=4cm}
\setlength\parindent{0cm}
\frenchspacing

% === FONT SETTINGS
% \defaultfontfeatures{Mapping=tex-text}
%~ \setmainfont {Sans Serif}
%~ \setsansfont {Serif}

\chead{\textit{Filip Bielejec - Curriculum Vitae}}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

\pagestyle{scrheadings}

\renewcommand{\headfont}{\normalfont\rmfamily\scshape}

% === FOOTER DEFINITION
\cofoot{
   %~ \addfontfeature{LetterSpace=20.0}\scshape\fontsize{9}{10}
   \footnotesize{
    \so{
        Route des Songenaz 9 · 744-00 Chamonix · France
}\\
        {\Large\Letter} fbielejec@gmail.com \ {\Large\Telefon} +32 487 443 064}%
}%

\begin{document}

%% \section{About Me}

%% I have been passionately building and writing computer programs for more than 10 years, in a wide range of areas and applications, from scientific software, visualization tools, mobile and distributed blockchain applications to systems for healthcare service providers.

%% I have worked on software written in R, Java, C/C++, JavaScript, Clojure and ClojureScript.
%% I have been very fortunate to have often worked with projects released to the public domain, therefore I could contribute to many Open Source projects and libraries, such as \href{https://github.com/district0x/memefactory}{memefactory}, \href{https://github.com/fbielejec/cljs-firebase-client}{cljs-firebase-client}, \href{https://github.com/fbielejec/lein-solc}{lein-solc}, and \href{https://github.com/fbielejec}{many more}.
%% %% \href{https://github.com/fbielejec/spread-server}{Spread}, \href{https://github.com/beagle-dev/beagle-lib}{Beagle}, \href{https://github.com/beast-dev/beast-mcmc}{Beast},

%% For the past 4 years I have been trying to do all the work I can in the functional programming paradigm, whenever it fits. % but I have a lot of OO experience as well.
%% I used to write a lot of R scripts, mainly for data-cleaning, analysis and vizializations, I especially enjoyed ggplot2 and went as far as writing desktop widgets in R by utilizing GTK bindings to R.
%% You can see some of that code \href{https://github.com/fbielejec/PlotMapsWidget}{here}, although at this time I can take no responsibility for whether it still works.

%% I maintain a blog dedicated mostly to Clojure / FP / DevOps: \url{https://www.blog.nodrama.io/} and I help to co-organize a \href{https://www.meetup.com/Leuven-Functional-Programming-Meetup/}{Functional Programming Meetup}.

%% I have a strong experience in devops, cloud networking, automation, monitoring, designing and deploying pipelines, mainly using AWS, Docker, Serverless, CircleCI and Travis.
%% I have worked on systems utilizing messaging, REST, EQL/GraphQL or even SOAP for communication.

%% %% I have always been driven by curiosity and although I have never worked professionally in Rust I have picked up an interest in it.
%% %% I'm especially interested in how it could be used for GPGPU programming, as well as it's use for low-level microcontrollers and embedded software.
%% %% Lately I started experimenting with the use of Rust with OpenCV: \url{https://github.com/fbielejec/eye-tracker} as a hobby-project.

%% I would love the opportunity to combine my past experience in data analysis and vizualization with my curiosity for functional programming and Clojure, hence this application.

%% work with Rust in larger systems (hence this application).

\begin{center}
\section{Education}
%% \vspace{-8pt}

\begin{lyxlist}{00.00.0000}
\item [{\noun{\scriptsize 2011 - 2015}}] \noun{KU Leuven,
Rega Institute For Medical Research, Evolutionary and Computational Virology }\\
\emph{Doctoral Training in Bioinformatics}
\item [{\noun{\scriptsize 2009-2010}}] \noun{Ghent University, Faculty
of Sciences, Department of Applied Mathematics and Computer Science}\\
\emph{Master of Statistical Data Analysis Programme}
\item [{\noun{\scriptsize 2005-2010}}] \noun{Technical University of \L{}ód\'{z},
Department of Technical Physics, Computer Science and Applied Mathematics}\\
\emph{Master in Mathematical Methods In Computer Science}
\end{lyxlist}

\section{Experiences}
\vspace{-8pt}

\begin{tabularx}{1.0\linewidth}{>{\raggedleft\scshape}p{2cm}X}

\gray Period    & \textbf{2021 - ongoing} \\
\gray Company  & \textbf{CardinalCryptography} \\
\gray Title & \textbf{Blockchain engineer} \\
\gray Languages & Rust, Python, Circom \\
\gray Keywords & ZeroKnowledge, SNARKs, Halo2 \\
\gray           &  {\textit{
Aleph Zero is a layer 1 privacy-enhancing blockchain that ensures scalability, low transaction fees, instant finality,
and optimal security.
In a part of multi-disciplinary team I was involved in the development of \href{https://mo.st/}{Most} bridge, \href{https://alephzero.org/the-button}{TheButton} smart-contract game.
Most importantly I was responsible for the development of the halo2 circuits underlying \href{https://docs.alephzero.org/aleph-zero/protocol-details/shielder}{Shielder}.
Shielder is a privacy-focused smart contract on Aleph Zero that uses zk-SNARKs to enable private transactions and interactions with DeFi by obscuring the link between user actions (deposits and withdrawals), making it impossible for the third-party observers to trace or associate these activities with specific users.
}} \\

\gray Period & \textbf{2020 - 2021} \\
\gray Company & \textbf{Clash} \\
\gray Title & \textbf{Cofounder \& Senior engineer} \\
\gray Languages & Clojure, ClojureScript, Java, Python, Rust \\
\gray Keywords & Mobile, AWS, Serverless \\
\gray           &  {\textit{
    \href{https://clashapp.co/}{Clash} is a mobile social-network application for sharing short videos.
     Within a team of 3 developers I was responsible for the analytics, design and development of an S3 data lake and an ingestion pipeline as well as a \href{https://www.youtube.com/watch?v=RG4g0Wd_elo&t=1s}{recommendations model}, powered by Rust, Spark and Tensorflow.
    %% Clash is a mobile social-network application for sharing short videos.
    %% Within a team of 3 developers I was responsible for the DevOps tasks, much of the backend and the data analytics, but I do not shy away from working on the client application either.
    %% The infrastructure is entirely serverless, with a mixture of scalable ECS tasks exchanging SQS messages and stateless Lambda functions.
    %% The API consists of \href{https://eql.readthedocs.io/en/latest/}{EQL} endpoints and communicates with the mobile clients over websocket connections to the AWS API Gateway.
    %% Persistance is achieved using MySQL and the hot storage uses Redis.
    %% The application code is written in ClojureScript targeting ReactNative, with a few components implemented natively.
    %% We use a pipeline composed of CloudFormation templates, Liquibase, Fastlane and CircleCI for automating the deployment.
    %% One of the sub-systems is
}} \\

\gray Period    & \textbf{2017 - 2020} \\
\gray Company  & \textbf{district0x} \\
\gray Title & \textbf{Clojure(Script) engineer} \\
\gray Languages & Clojure, ClojureScript, Solidity \\
\gray Keywords & Ethereum, IPFS, SmartContracts \\
\gray           &  {\textit{
    I helped building a network of decentralized OpenSource markets and communities, powered by Ethereum smart contracts written in Solidity on the backend and a suite of \href{https://github.com/district0x}{ClojureScript libraries} at the frontend.
    To build each `district' we experimented and tred out novel architectures that leveraged the decentralized nature of the Ethereum ecosystem.
}} \\

\gray Period    & \textbf{2017} \\
\gray Company  & \textbf{LambdaWerk GmbH} \hfill Berlin, Germany \\
\gray Title & \textbf{Functional Software Engineer} \\
\gray Languages & Clojure, ClojureScript \\
\gray           &  {\textit{Lambdawerk is a Berlin startup developing systems for the healthcare providers on the USA market, quering, combining and analyzing information from various data-sources.
%% our stack comprises entirely of Clojure and ClojureScript.
The software stack comprises of a MarkLogic NoSQL database for persistance, microservices use RabbitMQ messaging for communication and are exposed to the outside world using REST services.
Small team and fast paced environment demanded that I have worked on both frontend and backend applications, as well as on the infrastructure and DevOps needs.
}} \\

\gray Period    & \textbf{2016 - 2017} \\
\gray Company  & \textbf{Trimble T\&L} \hfill Haasrode Research-Park, Belgium \\
\gray Title & \textbf{Java Developer} \\
\gray Languages & Java, JavaScript, SQL \\
\gray           &  {\textit{I worked as part of a team developing applications for transport and logistics.
Our software collects and analyzes real-time information from on-board devices in trucks, including CAN bus, GPS and manually entered data, for a rela-time display in the dispatch centers.
My main involvment was the development of features allowing for the display of geo-awareness information on maps,
%% and co-development of a new application for the shipping of goods.
I was also responsible for migrating the security, authentication and user management from the legacy system to one utilizing \href{http://www.keycloak.org/}{Keycloak}.}} \\

\gray Period    & \textbf{2011 - 2016} \\
\gray Company  & \textbf{Rega Institute for Medical Research} \hfill Leuven, Belgium \\
\gray Job Title & \textbf{Researcher} \\
\gray Languages & Java, JavaScript, Clojure, R, Bash, C/C++, CUDA \\
\gray           &   {\textit {As s research-developer I was responsible for the development of open-source software for scientific analysis and visualisation of the spread of viruses over time and space.
    My main contributions are the advancements made to the high-performance parallel computations library \href{https://github.com/beagle-dev/beagle-lib}{Beagle}, development of novel models in \href{https://github.com/beast-dev/beast-mcmc}{BEAST}, and the development of \href{https://github.com/phylogeography/SpreaD3}{SpreaD3} software package.
    Driven by it's popularity, I still maintain \href{https://github.com/phylogeography/spread}{Spread} as an OpenSource project.}}
\end{tabularx}

\section{Skills}
%% \vspace{-8pt}

    \begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
    \gray Languages & {Rust, Clojure, ClojureScript, Python, Java, JavaScript, R, Solidity}\\

    \gray Libraries / Frameworks & {Rust: OpenCV (bindings), Tensorflow (bindings), polars, rayon, async-std, tokio, rusoto (AWS), serde, ron, tonic (gRPC).

                                    Python: keras, Tensorflow, Pandas, NumPy, pyspark.
                                    %% Java: Spring Boot, Hibernate, %JPA, GWT, EJB3, JSP %Processing, Spark, Gson,

                                    %% JavaScript: D3.js, React, Redux, ReactNative %Node.js, webpack,

                                    EVM: Solidity, Foundry.

                                    Clojure: Mount, Lacinia, Pedestal, Timbre, flow-storm, spec, hugSQL, transit, match.

                                    ClojureScript: Reagent, re-frame, garden.

                                    Stack: AWS, Serverless, Docker, CircleCI, GithubActions.
                                   }\\

 \gray Testing & {Clojure: kaocha, clj-kondo

                  ClojureScript: jest, doo, karma
 }\\

    \gray Security & {Keycloak}\\

    \gray Databases & {PostgreSQL, FireBase, Redis, Cassandra, ElasticSearch}\\

    \gray Database migration & {Liquibase, Lobos}\\

    \gray Deployment & {Serverless, Docker}\\

    \gray Messaging & {RabbitMQ, SQS, Kafka}\\

    \gray Operating systems & {Debian, Ubuntu, Linux Mint}\\

    \gray Other & {Revision control: git

                   Computer algebra systems: Maxima, Maple

                   Build systems: Maven, Leiningen, webpack, shadow-cljs, clojure-cli

                   Typesetting: $\mathrm{L\!\!^{_{{\scriptstyle A}}}\!\!\!\!\!\;\; T\!_{{\displaystyle E}}\! X}$

                   Dynamic report generation: Sweave, knitr, org-mode

                    %% Presentation: reveal.js, beamer

                   Microcontrollers: avrdude, arduino, TI Launchpad
                   }
    \end{tabularx}

\section{Training. Meetups \& Conferences}
%% \vspace{-8pt}

    \begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}

      \gray Date & \textbf{2022 - 2024}\\
      \gray Title  & \textbf{Polkadot Blockchain Academy} \hfill San Francisco, HongKong, Singapur \\
      & \emph{I was the \href{https://polkadot.com/blockchain-academy}{PBA} instructor for the Smart Contracts Module. My lectures and laboratories were focused on the exploits, MEV and other security considerations. For the final exercise students were tasked with findind and exploiting a vulnerability in a live smart contract. }
      \\
      
      \gray Date & \textbf{2017 - 2022}\\
      \gray Title  & \textbf{Leuven Functional Programming Meetup} \hfill Leuven, BE\\
      & \emph{I co-organize a \href{https://www.meetup.com/Leuven-Functional-Programming-Meetup/}{meetup} dedicated to discussing FP concepts and projects in a variety of languages and platforms: Clojure | Scala | Elixir | Elm | ClojureScript | Haskell. }
      \\

      \gray Date & \textbf{August 2 --- 3 2019}\\
      \gray Title  & \textbf{Heart Of Clojure} \hfill Leuven, BE\\
      & \emph{ A laid-back summer Conference for the European Clojure community }
      \\

             \gray Date & \textbf{June 13 --- 14 2017}\\
    \gray Title  & \textbf{Marklogic World} \hfill London, UK\\
           & \emph{Marklogic Enterprise NoSQL database conference.}
   \\

             \gray Date & \textbf{November 7 --- 11 2016}\\
    \gray Title  & \textbf{Devoxx} \hfill Antwerp, Belgium\\
           & \emph{Java Community Conference.}
   \\

             \gray Date & \textbf{April --- May 2013}\\
    \gray Title  & \textbf{Specialist Workshop on Parallel Computing} \hfill Leuven, Belgium\\
           & \emph{Series of workshops and seminars targeting important HPC topics, introduced by experts in the field.}
   \\

         \gray Date & \textbf{July 9 --- 27 2012}\\
    \gray Title  & \textbf{Summer Institute in Statistical Genetics} \hfill Seattle, WA, USA\\
           & \emph{Series of two-and-a-half day workshops designed to introduce statisticians to the statistical challenges posed by modern genetic data.}
   \\

        \gray Date & \textbf{July 9 --- 25 2012}\\
    \gray Title  & \textbf{Summer Institute in Statistics and Modelling in Infectious Diseases} \hfill Seattle, WA, USA\\
           & \emph{Series of two-and-a-half day workshops designed to introduce statisticians and mathematical modelers to the statistical and dynamic problems posed by modern infectious disease data.}
   \\

       \gray Date & \textbf{November 5 --- 6 2011}\\
    \gray Title  & \textbf{2 Day CUDA Workshop} \hfill Berlin, Germany\\
           & \emph{CUDA hands on workshop for developers who want to program and utilize Graphics Processing Units (GPU) using NVIDIA’s CUDA programming language.}
   \\

       \gray Date & \textbf{July 24 --- August 3 2011}\\
    \gray Title  & \textbf{Workshop on Computatonal Molecular Evolution} \hfill Woods Hole, MA, USA\\
           & \emph{Series of lectures, discussions and bioinformatic laboratories.}
   \\

       \gray Date & \textbf{May 5 --- 8 2011 }\\
    \gray Title  & \textbf{Processing Digital Environments} \hfill Lugano, Switzerland\\
           & \emph{Processing workshop about polymorphism and reflection.}
    \end{tabularx}

%      \section{Teaching experience}
% \vspace{-8pt}
%
%     \begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
%
%              \gray Date & \textbf{November 2013 --- February 2014}\\
%     \gray Title  & \textbf{Applied Biostatistics} \hfill KU Leuven, Belgium\\
%            & \emph{Teaching assistant, responsible for preparing and teaching excercise sessions.}
%    \\
%              \gray Date & \textbf{November 2013 --- February 2016}\\
%     \gray Title  & \textbf{Veme Bioinformatics workshop} \hfill Havana, Cuba\\
%            & \emph{Full-time teacher, responsible for preparing and teaching theory and excercise sessions.}
%    \\
%
%     \end{tabularx}

% \section{Grants \& Research support}
%  \vspace{-8pt}
% \begin{lyxlist}{00.00.0000}
% \item [{\noun{\scriptsize 2015 - 2016}}]
% \emph{Post-doctoral Mandate, Research Fund KU Leuven}
% \end{lyxlist}

\section{Some of my publications \& talks}
%% \vspace{-8pt}

\begin{lyxlist}{00.00.0000}

\item [{\noun{\scriptsize 2022}}] \emph{SPREAD 4: online visualisation of pathogen phylogeographic reconstructions}
K.D. Nahata, F. Bielejec, J. Monetta, S. Dellicour, A., Rambaut, M.A., Suchard, P. Lemey,
Virus evolution 8 (2), veac088
  
\item [{\noun{\scriptsize 2021}}] \emph{Making recommendations with Rust and Tensorflow }
\href{https://www.youtube.com/watch?v=RG4g0Wd_elo&t=1s}{Virtual Lunch \& Learn}

\item [{\noun{\scriptsize 2019}}] \emph{How to constrain your function inputs without the overhead of types? }
Functional Programming Meetup, Leuven, Belgium

\item [{\noun{\scriptsize 2017}}] \emph{(Quickly) securing your web applications with Keycloak. }
Clojure Dojo, Berlin, Germany

%% \item [{\noun{\scriptsize 2016}}] \emph{Identifying predictors of time-inhomogeneous viral evolutionary processess}
%% Bielejec, F., Baele, G., Rodrigo, Allen G., Suchard, M. A., Lemey, P.
%% Virus Evolution 2016, DOI: 10.1093/molbev/msw082

\item [{\noun{\scriptsize 2016}}] \emph{SpreaD3: interactive visualisation of spatiotemporal history and trait evolutionary processes}
Bielejec, F., Baele, G., Vrancken, B.,  Suchard, M. A., Rambaut, A., Lemey, P.
Molecular Biology and Evolution  2016, DOI: 10.1093/molbev/msw082

% \item [{\noun{\scriptsize 2016}}] \emph{The global antigenic diversity of swine influenza A viruses}
% Lewis, N.S., Russell, C.A., Langat, P., Anderson, T.K. Berger, K., Bielejec, F., et al
% eLife 2016, DOI:http://dx.doi.org/10.7554/eLife.12217

\item [{\noun{\scriptsize 2016}}] \emph{SpreaD3: User-friendly application to analyze and visualize phylodynamic reconstructions. }
Alphy 2016, Lille, France

%% \item [{\noun{\scriptsize 2016}}] \emph{Bayesian codon substitution modeling to identify sources of pathogen evolutionary rate variation}
%% Baele, G., Suchard, M. A., Bielejec, F., Lemey, P.
%% Microbial Genomics 2016, DOI: 10.1099/mgen.0.000057

% \item [{\noun{\scriptsize 2015}}] \emph{Host ecology determines the dispersal patterns of a plant virus}
% Trovão, N. S., Baele, G., Vrancken, B., Bielejec, F., Suchard, M. A., Fargette, D., Lemey, P.
% Virus Evol 2015, 1(1) DOI: 10.1093/ve/vev016

\item [{\noun{\scriptsize 2014}}] Poster: \emph{$\pi$BUSS: a parallel BEAST/BEAGLE utility for sequence simulation under complex evolutionary scenarios}
Mathematical and Computational Evolutionary Biology, Hameau de l'Etoile, France.

%% \item [{\noun{\scriptsize 2014}}] \emph{Inferring Heterogeneous Evolutionary Processes Through Time: from sequence substitution to phylogeography}
%% Bielejec, F., Lemey, P., Baele, G., Rambaut, A., Suchard, M.A.
%% Systematic Biology 2014, 63(4), 493-504

\item [{\noun{\scriptsize 2013}}] \emph{$\pi$BUSS: a parallel BEAST/BEAGLE utility for sequence simulation under complex evolutionary scenarios}
Bielejec, F., Lemey, P., Carvalho, L.M., Baele, G., Rambaut, A., Suchard, M.A.
BMC Bioinformatics 2014, 15:133

\item [{\noun{\scriptsize 2013}}] \emph{Inferring large-scale heterogeneous evolutionary processes through time}
Mathematical and Computational Evolutionary Biology, Hameau de l'Etoile, France.

%% \item [{\noun{\scriptsize 2013}}] \emph{Presenting SPREAD: Spatial Phylogenetic Reconstruction of Evolutionary Dynamics}
%% Bioinformatics Group Meeting (BIG), Leuven, Belgium.

%% \item [{\noun{\scriptsize 2012}}] \emph{Unifying viral genetics and human transportation data to predict the global transmission dynamics of human influenza H3N2}
%% Lemey, P., Rambaut, A., Bedford, T., Faria, N.R., Bielejec, F., Baele, G., Russell, C.A., Smith, D.J., Pybus, O.G., Brockmann, D., Suchard, M. A.
%% PLoS pathogens 10(2), e1003932

\item [{\noun{\scriptsize 2012}}] \emph{Massive parallelization of likelihood computations through graphics processing units.}
Genome Bioinformatics Meeting, Leuven, Belgium.

% \item [{\noun{\scriptsize 2012}}] \emph{A counting renaissance: Combining stochastic mapping and empirical Bayes to quickly detect amino acid sites under positive selection.}
% Lemey, P., Bielejec, F., Suchard, M. A., Minin, V., Kosakovsky Pond, S.L.
% Bioinformatics 28(24), 3248-56

%% \item [{\noun{\scriptsize 2011}}] \emph{Spatial phylogenetic reconstruction of evolutionary dynamics.}
%% ERC Working Group Meeting, Edinburgh, Scotland.

%% \item [{\noun{\scriptsize 2011}}] \emph{SPREAD: Spatial phylogenetic reconstruction of evolutionary dynamics.}
%% Bielejec, F., Rambaut, A., Suchard, M. A., Lemey, P.
%% Bioinformatics 27(20), 2910-2912.

\end{lyxlist}

%~ \section{Languages}
%~ \vspace{-8pt}
%~
%~ \begin{lyxlist}{MMMMM}
%~ \item [{~}] {Polish (native), English (fluent), German(intermediate), Dutch (beginner)}
%~ \end{lyxlist}
%~
%~ \section{Interests}
%~ \vspace{-8pt}
%~
%~ \begin{lyxlist}{MMMMM}
%~ \item [{~}] {Statistics, data analysis, programming and algorithms}
%~ \end{lyxlist}


 %\section{References}
 % \vspace{-8pt}

% \begin{lyxlist}{00.00.0000}
% \item [{\noun{\scriptsize Professor Philippe Lemey}}]  \emph{philippe.lemey@gmail.com }
%
% \item [{\noun{\scriptsize Professor Marc Suchard}}]  \emph{msuchard@ucla.edu }
%
% \item [{\noun{\scriptsize Professor Anne-Mieke Vandamme}}] \emph{annemie.vandamme@kuleuven.be }
%\end{lyxlist}


\section{Social}
  %% \vspace{-8pt}

 \begin{lyxlist}{00.00.0000}

 \item [{\noun{\scriptsize Blog}}] \emph{ \url{https://www.blog.nodrama.io/} }

 \item [{\noun{\scriptsize Github}}] \emph{ \url{http://github.com/fbielejec} }

 \item [{\noun{\scriptsize StackOverflow}}] \emph{ \url{http://stackoverflow.com/users/813216/fbielejec }}

\end{lyxlist}

\end{center}

\end{document}
